Self-interacting dark matter model without dark energy in cosmology

### 2024-12-27 article/article.tex
solution singularity?

   The $L_X-L_{UV}$ relation of quasar is usually written as
   \begin{equation}
      L_X=\beta+\gamma\log L_{UV},
   \end{equation}
   which gives that
   \begin{eqnarray}
      \nonumber\log_{10}(F_X)&=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
                    \\ &+2(\gamma-1)\log_{10}(d_L),
   \end{eqnarray}
   where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
   So the $\chi^2$ function for the QSO data can be defined as
   \begin{equation}
      \chi_{\text{QSO}}^2=\sum_i^{2421}\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
      -\ln(2\pi s_i^2),
   \end{equation}
   where $s_i^2=\mathrm{d}y_i^2+\gamma^2\mathrm{d}x_i^2+\delta^2$ refers to the 
   uncertainties on the $x_i\ (\log_{10}F_X)$ and $y_i\ (\log_{10}F_{UV})$ and
   $\delta_i$ reprensent the instrinsic dispersion.

@@

   However, the Eq.(\ref{eq:8}) just have a stiff point when $z\to\infty$, so the IDM
   model can not give a constraint to the $r_{\text{d}}$ and we just try to use the cross
   parameter $r_{\text{d}}h$ to give the constraints.

@@

   \begin{table}[htbp]
      \caption{Parameters and priors used in analysis}
      \centering
      \begin{tabular}{lll}
         \hline\hline
         parameter & initial & prior \\
         \hline
         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
         $n$ & --- & $\mathcal{U}[-10,10]$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
         $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
         \hline
         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
         \hline
         $\beta$ & $-11$ & $\mathcal{U}[-15,-5]$ \\
         $\gamma$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
         \hline
      \end{tabular}
      \label{tab:4}
   \end{table}

@@

>>>>

   The $L_X-L_{UV}$ relation of quasar is usually written as
   \begin{equation}
      \log_{10}(L_X)=\beta+\gamma\log_{10}(L_{UV}),
   \end{equation}
   which gives that
   \begin{eqnarray}
      \nonumber\log_{10}(F_X)&=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
                    \\ &+2(\gamma-1)\log_{10}(d_L),
   \end{eqnarray}
   where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
   Here we use the parameters defined in \cite{li2024redshiftevolutionxrayuv}, which
   gives\begin{equation}
      \beta=\beta_0+\beta_1(1+z),\gamma=\gamma_0+\gamma_1(1+z),
   \end{equation}
   so the $\chi^2$ function for the QSO data can be defined as
   \begin{equation}
      \chi_{\text{QSO}}^2=\sum_i^{2421}\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
      -\ln(2\pi s_i^2)\right],
   \end{equation}
   where $s_i^2=\mathrm{d}y_i^2+\gamma^2\mathrm{d}x_i^2+\delta^2$ refers to the 
   uncertainties on the $x_i\ (\log_{10}F_X)$ and $y_i\ (\log_{10}F_{UV})$ and
   $\delta_i$ reprensent the instrinsic dispersion.

@@

   However, the Eq.(\ref{eq:8}) just have a singularity when $z\to\infty$, so the IDM
   model can not give a constraint to the $r_{\text{d}}$ and we just try to use the cross
   parameter $r_{\text{d}}h$ to give the constraints.

@@

   \begin{table}[htbp]
      \caption{Parameters and priors used in analysis}
      \centering
      \begin{tabular}{lll}
         \hline\hline
         parameter & initial & prior \\
         \hline
         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
         $n$ & 0 & $\mathcal{U}[-10,10]$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
         $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
         \hline
         $\beta_0$ & 6 & $\mathcal{U}[-15,15]$ \\
         $\beta_1$ & 1 & $\mathcal{U}[-10,10]$ \\
         $\gamma_0$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
         $\gamma_1$ & 0 & $\mathcal{U}[-1.0,1.0]$ \\         
         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
         \hline
         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
         \hline
      \end{tabular}
      \label{tab:4}
   \end{table}

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{qso_fx_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{qso_fx_2.pdf}
      }
      \caption{The constraint result from the quasar data}
   \end{figure}
